News Across Languages - Cross-Lingual Document Similarity and Event Tracking

### 2015-09-03 rupnik2015.tex
idf

We also used a term re-weighting scheme that adjusts for the fact that some words occur more frequently in general. A term weight should correspond to the importance of the term for the given corpus. The common weighting scheme is called \emph{Term Frequency Inverse Document Frequency} ($TFIDF$) weighting. An \emph{Inverse Document Frequency} ($IDF$) weight for the dictionary term $k$ is defined as $\log\left( \frac{N}{DF_k} \right)$, where $DF_k$ is the number of documents in the corpus which contain term $k$. \todo{our corpus is dynamic how do we deal with this?} Therefore we can definte a document's $TFIDF$ as
$$ x_{ij}  := \frac{\mbox{term frequency in document } i}{\mbox{inverse document frequency of term } j}.$$
The $TFIDF$ weighted vector space model document representation corresponds to a map $\phi : \text{text} \rightarrow \RR^n$ defined by:
$$\phi(d)_k = {TF}_k(d) \log\left( \frac{N}{{DF}_k}\right).$$

>>>>

We also used a term re-weighting scheme that adjusts for the fact that some words occur more frequently in general. A term weight should correspond to the importance of the term for the given corpus. The common weighting scheme is called \emph{Term Frequency Inverse Document Frequency} ($TFIDF$) weighting. An \emph{Inverse Document Frequency} ($IDF$) weight for the dictionary term $k$ is defined as $\log\left( \frac{N}{DF_k} \right)$, where $DF_k$ is the number of documents in the corpus which contain term $k$. 
When building cross-lingual models, the IDF scores were computed with respect to the Wikipedia corpus. In the other part of our system, we computed TFIDF vectors on streams of news documents in multiple languages. There the IDF scores for each language changed dynamically - for each new document we computed the IDF of all news articles within a 10 day window.

Therefore we can define a document's $TFIDF$ as
$$ x_{ij}  := \frac{\mbox{term frequency in document } i}{\mbox{inverse document frequency of term } j}.$$
The $TFIDF$ weighted vector space model document representation corresponds to a map $\phi : \text{text} \rightarrow \RR^n$ defined by:
$$\phi(d)_k = {TF}_k(d) \log\left( \frac{N}{{DF}_k}\right).$$
